The LSST-DESC 3x2pt Tomography Optimization Challenge

### 2021-08-05 paper/paper.tex
add author statement and standard acks

\section{Acknowledgements}
ESC acknowledges support from the FAPESP (\#2019/19687-2) and CNPq  (\#308539/2018-4).
AHW is supported by a European Research Council Consolidator Grant (No. 770935).

>>>>

\section{Acknowledgements}

This paper has undergone internal review in the LSST Dark Energy Science Collaboration.
The internal reviewers were Markus Michael Rau, Christopher Morrison, and Shahab Joudaki.

ESC acknowledges support from the FAPESP (\#2019/19687-2) and CNPq  (\#308539/2018-4).
AHW is supported by a European Research Council Consolidator Grant (No. 770935).

The DESC acknowledges ongoing support from the Institut National de
Physique Nucl\'eaire et de Physique des Particules in France; the
Science \& Technology Facilities Council in the United Kingdom; and the
Department of Energy, the National Science Foundation, and the LSST
Corporation in the United States.  DESC uses resources of the IN2P3
Computing Center (CC-IN2P3--Lyon/Villeurbanne - France) funded by the
Centre National de la Recherche Scientifique; the National Energy
Research Scientific Computing Center, a DOE Office of Science User
Facility supported by the Office of Science of the U.S.\ Department of
Energy under Contract No.\ DE-AC02-05CH11231; STFC DiRAC HPC Facilities,
funded by UK BIS National E-infrastructure capital grants; and the UK
particle physics grid, supported by the GridPP Collaboration.  This
work was performed in part under DOE Contract DE-AC02-76SF00515

\subsection{Author Contributions}
Zuntz led the project, ran the challenge, wrote most paper text, and made plots.
Lanusse submitted methods, made plots, and contributed to metrics, infrastructure, analysis, and conclusions.
Malz and Wright submitted methods, made plots, and contributed to analysis and conclusions.
Slosar submitted methods, wrote initial infrastructure, and assisted with challenge design.
Authors Abolfathi to Teixeira submitted methods to the challenge.
Subsequent authors generated the data used in the challenge and contributed to infrastructure used in the project.

Authors AP, CRB, ESC, BMOF, EJG, and GT are collaborators from outside the
Dark Energy Science Collaboration included here under a DESC publication policy exemption.
